---
title: "Coursera Developing Data Products Week 2 Assignment"
author: "Spinwing"
date: "3 November 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## UNESCO World Heritage Monuments in Italy

As part of the Coursera Developing Data Products, students have to publish a web page featuring a leaflet map.

Why not show something cultural? Being Italian, I know that my country hosts quite a few monuments declared UNESCO World Heritage.

Enjoy an updated list. Maybe one day, you will come to Italy and visit them. In the meantime, I'm checking the list to see which ones I've not visited yet ;)

Data courtesy ofUNESCO/World Heritage Centre. Copyright © 1992 - 2017 - All rights reserved
Source : : http://whc.unesco.org/en/syndication

```{r map, echo=FALSE, warning=FALSE, message=FALSE}
library(leaflet)
whc_sites_2017 <- read.csv("whc-sites-2017.csv") 
whc_sites_2017 %>% leaflet() %>% addTiles() %>% addMarkers(popup = whc_sites_2017$name_en)
```
